Results

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
replaced 'looked to see'

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).

>>>>

To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).
